---
title: "HW1"
output: github_document
date: '2022-09-24'
---

## How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r}
library(dplyr)
library(nycflights13)
library(ggplot2)
flights %>%
  mutate(missing_dep_time = if_else(condition= is.na(dep_time),
                                    true=T,
                                    false=F)) %>%
  summarize(flights_missing_dep_time = sum(missing_dep_time))
filter(flights, is.na(dep_time))

#Missing dep_delay, arr_time, arr_delay, air_time, perhaps represent canceled flights.
```

##Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
flights %>%
  mutate(dep_time = as.integer(dep_time/100) * 60 + dep_time%%100,
         sched_dep_time = as.integer(sched_dep_time/100) * 60 + sched_dep_time%%100)
```
##Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()
```{r}
flights %>%
  group_by(month, day) %>%
  summarize(average_dep_delay = mean(dep_delay,na.rm=TRUE),
                                     proportion_canceled  = sum(is.na(dep_time)/n())) %>%
  ggplot(mapping = aes(x = average_dep_delay, y = proportion_canceled)) +
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE)
  #Yes they are related. More canceled flights leads to more delay.
```